### 2020-10-08 input/background.tex
text of figure

\begin{definition}[Logical partitions]
  A logical \underline{p}artition $P_s$ originated at a
  \underline{s}ource process $s \in V$ is a set of interconnected
  processes that do not belong to another logical partition.
\end{definition}

@@

When $distance$ involves monotonically increasing scalars such as
latency or number of hops between sources and processes, the optimal
partitioning consists in processing the multiple destinations shortest
path~\REF at each process. \TODO{Easy to solve when all processes
  receives all messages.}

Algorithm~\ref{algo:add} shows the instructions of dynamic
partitioning where the only operation available to processes is the
adding of a partition.  Line~\ref{line:lowestbound} shows the lowest
bound. Line~\ref{line:accumulator} shows the accumulator.

\begin{algorithm}
  \input{input/algoadd.tex}
  \caption{\label{algo:add}Adding partitions by Process $p$.}
\end{algorithm}

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:addA}Both Process $a$ and
      Process $c$ initiate a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figaddA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:addB}Messages transit through communication
      links and carry increasing weights.]{\input{input/figaddB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:addC}Process $b$ receives and forwards
      $Add_{c, +1}$ then discards $Add_{a, +1.5}$, for the latter distance
      is higher.]{\input{input/figaddC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:addD}Processes $b$, $c$, and $d$ discard
      incoming messages. The system converged to optimal partitions.]{
      \input{input/figaddD.tex}}
    \caption{\label{fig:add}Simple accumulation in messages makes the
      system converge to optimal partitions with contained
      flooding.}
  \end{center}
\end{figure*}

@@

>>>>

\begin{definition}[Logical partition]
  A logical \underline{p}artition $P_s$ originated at a
  \underline{s}ource process $s \in V$ is a set of interconnected
  processes that do not belong to another logical partition.
\end{definition}

@@

When $distance$ involves monotonically increasing scalars such as
latency or number of hops between sources and processes, the optimal
partitioning consists in processing the multiple destinations shortest
path~\REF at each process.  Algorithm~\ref{algo:add} shows the
instructions of such dynamic partitioning where the only operation
available to processes is the adding of a
partition. Figure~\ref{fig:add} illustrates its behavior on a system
comprising 4 processes $a$, $b$, $c$, and $d$. Two processes $a$ and
$c$ concurrently create a partition. They initialize their own state
with the lowest possible bound $0$ (see Line~\ref{line:lowestbound}),
and send a message to each of their neighbors by accumulating the
corresponding edge weight (see Line~\ref{line:accumulator}). In
Figure~\ref{fig:addC}, Process $b$ receives $Add_{c, 1}$. Since it
improves its own partition distance, it keeps it and forwards it to
its neighbors. Process $b$ discards $Add_{b, 1.5}$, for it does not
improve its partition distance. Processes $c$ and $d$ will never hear
of Process $a$'s partition. In Figure~\ref{fig:addD}, processes
discard last transiting messages. The system converged to the optimal
partitioning.

\begin{algorithm}
  \input{input/algoadd.tex}
  \caption{\label{algo:add}Adding a partition by Process $p$.}
\end{algorithm}

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:addA}Both Process $a$ and
      Process $c$ initiate a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figaddA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:addB}Messages transit through communication
      links and carry increasing weights.]{\input{input/figaddB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:addC}Process $b$ receives and forwards
      $Add_{c, +1}$ then discards $Add_{a, +1.5}$, for the latter distance
      is higher.]{\input{input/figaddC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:addD}Processes $b$, $c$, and $d$ discard
      incoming messages. The system converged to optimal partitions.]{
      \input{input/figaddD.tex}}
    \caption{\label{fig:add}Simple accumulation in messages makes the
      system converge to optimal partitions with contained
      broadcast.}
  \end{center}
\end{figure*}

@@

Order on the broadcast.
